Three 38 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-15 papers/ms.tex
update ms

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities of candidate members of the
    Cep-Her complex.}
	{\it Top row}: On-sky positions in galactic coordinates.
	Black points are stars for which membership is more likely than for
	gray points (``weight'' cuts above 0.10 and 0.02 respectively; see text).
	The $\delta$ Lyr cluster, at $\{ l, b\} \approx \{ 66^\circ, 12^\circ\}$, contains Kepler-1627  \citep{bouma_kep1627_2022}.
	{\it Middle row}:
	Galactic positions.
	The Sun is at $\{X, Y, Z\} = \{-8122, 0, 20.8\}$ pc.
	{\it Bottom row}:
	Galactic tangential velocities.
	The spatial and kinematic overlap between RSG-5 ($\{ l, b\} \approx \{ 82^\circ, 6^\circ\}$; $\{ X, Y, Z\} \approx \{-8070, 330, 50\} $ pc)
	and Kepler-1643 is fairly obvious.
	KOI-7368 and KOI-7913 however are candidate members of a diffuse population,
	that we dub ``CH-2''.
	Although CH-2 appears close to RSG-5 when projected in $(X,Y)$ and $(v_b, v_{l*})$,
	it is spatially  distinct in $(Z,Y)$.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2a.pdf}
			\includegraphics[width=0.469\textwidth]{f2b.pdf}
		}

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Positions  and velocities of candidate members of the
    Cep-Her complex.}
	{\it Top row}: On-sky positions in galactic coordinates.
	Black points are stars for which group membership is more likely than for
	gray points (``weight'' cuts above 0.10 and 0.02; see text).
	Kepler-1627 is in the outskirts of the $\delta$ Lyr cluster  \citep{bouma_kep1627_2022}, which is centered
	at $\{ l, b\} \approx \{ 66^\circ, 12^\circ\}$.
	{\it Middle row}:
	Galactic positions.
	The Sun is at $\{X, Y, Z\} = \{-8122, 0, 20.8\}$ pc.
	{\it Bottom row}:
	Galactic tangential velocities (left) and longitudinal tangential velocity
	versus galactic latitude (right).
	There is a strong spatial and kinematic overlap between Kepler-1643
  and RSG-5 (purple points; $\{ l, b\} \approx \{ 82^\circ, 6^\circ\}$; $\{ X, Y, Z\}
  \approx \{-8070, 330, 50\} $ pc).
	KOI-7368 and KOI-7913 however are candidate members of a diffuse population,
	that we dub ``CH-2'' (green points).
	The green and purple points are manually selected from the initial candidate
	population based on galactic position and tangential velocity.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2a.pdf}
			\includegraphics[width=0.49\textwidth]{f2b.pdf}
		}
